### 2016-05-01 ThesisJo/introduction.tex
Working on the review
la2pdf commit - 2016:05:01	20:45:42	(sø. 1.mai)

@@

>>>>

Faster, smarter, better.

Preface?

Perhaps the most advanced trait of human intelligence is the ability of ask why. We are masters at both understanding what a problem is, as well as finding solutions to it.

What if we could create intelligent machines?

When we face a problem we do not understand, To understand what the problem is

This thesis will eventially narrow down to adaptive processing sonar images, and technicalities of the implementation process.

@@

There is no best algorithm/system for all tasks. Best would be to use them all as they complement each other.

Hard to determine the most vital information in an image. The better the image the more information is contains, and the more processing power and memory bandwidth is needed to handle it.
